---
title: "MSDS_7330_Project"
author: "Javier Saldaña"
date: "February 4, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(RCurl)
library(dplyr)
library(tidyr)
library(forecast)
library(ggplot2)
library(dygraphs)
library(leaps)
library(ISLR)
library(reshape)
```

##Data Description

The data used for this project was sourced from finance.yahoo.com. There are over 440 data sets for various companies in the S&P 500 index. Each data set contains the following fields:
"Date"  "Open"  "High"  "Low" "Close" "Adj Close" "Volume"

The "Date" field contains entries for every day the stock was active. It beings from the earliest date on record and ends on Feb. 1, 2019, which is the last day the market was open before the data set was extracted.

The "Open" field pertains to the stock price at the point the market opened.

The "High" field pertains to the maximum stock price for that day.

The "Low" field pertains to the minimum stock price for that day.

The "Close" field pertains to the stock price at the point the market closed for the day.

The "Adj Close" field displays the closing price of the stock during after-hours trading

```{r}
#A
SP500 <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/A.csv"), header = TRUE) [ ,1:2]
colnames(SP500)[2] <- "A"

#AAL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AAL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AAL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#AAP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AAP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AAP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#AAPL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AAPL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AAPL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#ABC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ABC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ABC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#ABMD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ABMD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ABMD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#ABT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ABT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ABT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#ACN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ACN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ACN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#ADBE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ADBE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ADBE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

#ADI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ADI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ADI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ADM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ADM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ADM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ADP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ADP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ADP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ADS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ADS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ADS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ADSK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ADSK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ADSK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AEE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AEE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AEE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AEP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AEP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AEP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AES
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AES.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AES"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AFL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AFL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AFL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AGN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AGN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AGN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AIG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AIG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AIG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AIV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AIV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AIV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AIZ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AIZ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AIZ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AJG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AJG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AJG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AKAM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AKAM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AKAM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ALB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ALB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ALB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ALGN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ALGN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ALGN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ALK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ALK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ALK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ALL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ALL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ALL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ALXN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ALXN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ALXN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMAT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMAT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMAT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AME
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AME.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AME"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMGN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMGN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMGN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AMZN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AMZN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AMZN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ANSS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ANSS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ANSS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ANTM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ANTM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ANTM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AON
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AON.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AON"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AOS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AOS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AOS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#APA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/APA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "APA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#APC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/APC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "APC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#APD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/APD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "APD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#APH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/APH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "APH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ARE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ARE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ARE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ARNC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ARNC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ARNC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ATVI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ATVI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ATVI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AVB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AVB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AVB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AVY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AVY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AVY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AWK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AWK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AWK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AXP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AXP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AXP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#AZO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/AZO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "AZO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BAC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BAC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BAC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BAX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BAX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BAX"
stock<-stock[-(which(stock$BAX == "null")),] #remove manual null values
stock$BAX <- as.numeric(as.character(stock$BAX)) #convert to numeric
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BBT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BBT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BBT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BBY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BBY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BBY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BDX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BDX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BDX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BEN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BEN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BEN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BF-B
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BF-B.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BF-B"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BHGE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BHGE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BHGE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BIIB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BIIB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BIIB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BKNG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BKNG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BKNG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BLK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BLK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BLK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BLL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BLL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BLL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BMY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BMY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BMY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BRK-B
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BRK-B.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BRK-B"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BSX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BSX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BSX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BWA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BWA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BWA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#BXP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/BXP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "BXP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#C
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/C.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "C"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CAG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CAG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CAG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CAH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CAH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CAH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CAT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CAT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CAT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CBRE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CBRE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CBRE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CBS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CBS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CBS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CCI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CCI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CCI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CCL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CCL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CCL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CDNS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CDNS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CDNS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CELG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CELG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CELG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CERN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CERN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CERN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CFG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CFG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CFG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CHD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CHD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CHD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CHRW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CHRW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CHRW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CINF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CINF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CINF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CLX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CLX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CLX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CMA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CMA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CMA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CMCSA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CMCSA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CMCSA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CME
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CME.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CME"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CMG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CMG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CMG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CMI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CMI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CMI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CMS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CMS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CMS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CNC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CNC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CNC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CNP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CNP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CNP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#COF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/COF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "COF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#COG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/COG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "COG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#COO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/COO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "COO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#COP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/COP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "COP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#COST
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/COST.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "COST"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CPB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CPB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CPB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CPRT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CPRT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CPRT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CRM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CRM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CRM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CSCO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CSCO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CSCO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CSX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CSX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CSX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CTAS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CTAS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CTAS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CTL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CTL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CTL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CTSH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CTSH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CTSH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CTXS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CTXS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CTXS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CVS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CVS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CVS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#CVX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/CVX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "CVX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#D
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/D.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "D"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DHI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DHI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DHI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DHR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DHR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DHR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DIS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DIS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DIS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DISCA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DISCA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DISCA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DISH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DISH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DISH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DLTR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DLTR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DLTR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DOV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DOV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DOV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DRE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DRE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DRE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DRI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DRI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DRI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DTE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DTE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DTE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DUK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DUK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DUK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DVA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DVA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DVA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DVN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DVN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DVN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DWDP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DWDP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DWDP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#DXC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/DXC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DXC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EBAY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EBAY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EBAY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ECL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ECL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ECL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ED
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ED.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ED"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EFX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EFX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EFX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EIX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EIX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EIX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EMN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EMN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EMN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EMR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EMR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EMR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EOG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EOG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EOG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EQIX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EQIX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EQIX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EQR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EQR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EQR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ES
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ES.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ES"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ESS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ESS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ESS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ETFC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ETFC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ETFC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ETN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ETN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ETN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ETR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ETR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ETR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EXC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EXC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EXC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EXPD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EXPD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EXPD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EXPE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EXPE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EXPE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#EXR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/EXR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "EXR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#F
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/F.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "F"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FAST
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FAST.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FAST"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FCX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FCX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FCX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FDX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FDX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FDX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FFIV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FFIV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FFIV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FIS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FIS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FIS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FISV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FISV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FISV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FITB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FITB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FITB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FLIR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FLIR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FLIR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FLR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FLR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FLR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FLS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FLS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FLS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FMC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FMC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FMC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FOX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FOX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FOX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FOXA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FOXA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FOXA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FRT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FRT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FRT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#FTI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/FTI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "FTI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GILD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GILD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GILD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GIS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GIS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GIS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GLW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GLW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GLW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GOOG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GOOG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GOOG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GPC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GPC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GPC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GPN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GPN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GPN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GPS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GPS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GPS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GRMN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GRMN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GRMN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#GWW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/GWW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GWW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HAL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HAL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HAL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HAS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HAS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HAS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HBAN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HBAN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HBAN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HBI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HBI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HBI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HCP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HCP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HCP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HES
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HES.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HES"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HFC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HFC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HFC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HIG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HIG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HIG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HOG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HOG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HOG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HOLX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HOLX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HOLX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HON
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HON.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HON"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HPQ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HPQ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HPQ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HRB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HRB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HRB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HRL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HRL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HRL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HRS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HRS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HRS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HSIC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HSIC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HSIC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HST
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HST.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HST"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HSY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HSY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HSY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#HUM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/HUM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "HUM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IBM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IBM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IBM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ICE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ICE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ICE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IDXX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IDXX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IDXX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IFF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IFF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IFF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ILMN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ILMN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ILMN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#INCY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/INCY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "INCY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#INTC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/INTC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "INTC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#INTU
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/INTU.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "INTU"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IPG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IPG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IPG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IPGP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IPGP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IPGP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IRM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IRM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IRM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ISRG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ISRG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ISRG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ITW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ITW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ITW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#IVZ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/IVZ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IVZ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JBHT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JBHT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JBHT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JCI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JCI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JCI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JEC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JEC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JEC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JEF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JEF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JEF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JKHY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JKHY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JKHY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JNJ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JNJ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JNJ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JNPR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JNPR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JNPR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JPM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JPM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JPM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#JWN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/JWN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "JWN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#K
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/K.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "K"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KEY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KEY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KEY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KIM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KIM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KIM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KLAC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KLAC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KLAC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KMB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KMB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KMB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KMX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KMX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KMX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KSS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KSS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KSS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#KSU
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/KSU.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "KSU"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#L
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/L.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "L"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LEG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LEG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LEG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LEN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LEN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LEN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LKQ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LKQ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LKQ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LLL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LLL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LLL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LLY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LLY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LLY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LMT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LMT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LMT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LNC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LNC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LNC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LNT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LNT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LNT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LOW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LOW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LOW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LRCX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LRCX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LRCX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#LUV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/LUV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "LUV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#M
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/M.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "M"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MAA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MAA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MAA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MAC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MAC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MAC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MAR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MAR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MAR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MAS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MAS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MAS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MAT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MAT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MAT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MCD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MCD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MCD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MCHP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MCHP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MCHP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MCK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MCK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MCK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MCO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MCO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MCO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MDLZ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MDLZ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MDLZ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MDT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MDT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MDT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MET
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MET.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MET"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MGM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MGM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MGM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MHK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MHK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MHK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MKC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MKC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MKC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MLM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MLM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MLM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MMC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MMC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MMC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MMM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MMM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MMM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MNST
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MNST.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MNST"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MOS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MOS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MOS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MRK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MRK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MRK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MRO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MRO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MRO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MSFT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MSFT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MSFT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MSI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MSI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MSI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MTB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MTB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MTB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MTD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MTD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MTD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MU
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MU.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MU"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MXIM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MXIM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MXIM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#MYL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/MYL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "MYL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NBL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NBL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NBL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NDAQ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NDAQ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NDAQ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NEE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NEE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NEE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NEM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NEM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NEM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NFLX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NFLX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NFLX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NFX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NFX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NFX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NKE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NKE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NKE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NKTR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NKTR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NKTR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NOC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NOC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NOC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NOV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NOV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NOV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NRG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NRG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NRG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NTAP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NTAP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NTAP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NTRS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NTRS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NTRS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NUE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NUE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NUE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NVDA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NVDA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NVDA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#NWL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/NWL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "NWL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#O
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/O.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "O"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#OKE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/OKE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "OKE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#OMC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/OMC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "OMC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ORCL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ORCL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ORCL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ORLY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ORLY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ORLY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#OXY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/OXY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "OXY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PAYX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PAYX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PAYX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PBCT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PBCT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PBCT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PCAR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PCAR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PCAR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PEG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PEG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PEG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PEP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PEP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PEP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PFE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PFE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PFE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PFG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PFG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PFG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PHM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PHM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PHM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PKG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PKG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PKG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PKI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PKI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PKI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PLD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PLD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PLD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PNC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PNC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PNC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PNR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PNR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PNR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PNW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PNW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PNW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PPL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PPL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PPL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PRGO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PRGO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PRGO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PRU
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PRU.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PRU"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PSA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PSA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PSA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PVH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PVH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PVH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PWR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PWR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PWR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#PXD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/PXD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "PXD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#QCOM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/QCOM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "QCOM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RCL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RCL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RCL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#REG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/REG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "REG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#REGN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/REGN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "REGN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RHI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RHI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RHI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RHT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RHT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RHT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RJF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RJF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RJF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RMD
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RMD.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RMD"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ROK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ROK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ROK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ROL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ROL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ROL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ROP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ROP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ROP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ROST
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ROST.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ROST"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RSG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RSG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RSG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#RTN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/RTN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "RTN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SBAC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SBAC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SBAC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SBUX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SBUX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SBUX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SCHW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SCHW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SCHW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SEE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SEE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SEE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SHW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SHW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SHW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SIVB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SIVB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SIVB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SJM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SJM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SJM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SLB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SLB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SLB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SLG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SLG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SLG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SNA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SNA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SNA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SNPS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SNPS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SNPS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SPG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SPG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SPG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SPGI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SPGI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SPGI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SRE
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SRE.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SRE"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#STI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/STI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "STI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#STT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/STT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "STT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#STX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/STX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "STX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#STZ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/STZ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "STZ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SWK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SWK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SWK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SWKS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SWKS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SWKS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SYF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SYF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SYF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SYK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SYK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SYK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SYMC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SYMC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SYMC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#SYY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/SYY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "SYY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#T
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/T.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "T"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TAP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TAP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TAP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TDG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TDG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TDG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TFX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TFX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TFX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TGT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TGT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TGT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TIF
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TIF.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TIF"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TJX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TJX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TJX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TMK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TMK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TMK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TMO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TMO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TMO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TPR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TPR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TPR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TROW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TROW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TROW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TRV
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TRV.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TRV"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TSCO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TSCO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TSCO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TSN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TSN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TSN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TSS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TSS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TSS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TTWO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TTWO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TTWO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TXN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TXN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TXN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#TXT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/TXT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "TXT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UAA
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UAA.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UAA"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UAL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UAL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UAL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UDR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UDR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UDR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UHS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UHS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UHS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UNH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UNH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UNH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UNM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UNM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UNM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UNP
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UNP.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UNP"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UPS
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UPS.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UPS"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#URI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/URI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "URI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#USB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/USB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "USB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#UTX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/UTX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "UTX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VAR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VAR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VAR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VFC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VFC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VFC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VIAB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VIAB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VIAB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VLO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VLO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VLO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VMC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VMC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VMC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VNO
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VNO.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VNO"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VRSN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VRSN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VRSN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VRTX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VRTX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VRTX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VTR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VTR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VTR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#VZ
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/VZ.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "VZ"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WAT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WAT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WAT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WCG
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WCG.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WCG"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WDC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WDC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WDC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WEC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WEC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WEC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WELL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WELL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WELL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WFC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WFC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WFC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WHR
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WHR.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WHR"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WLTW
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WLTW.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WLTW"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WMB
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WMB.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WMB"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WMT
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WMT.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WMT"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WRK
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WRK.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WRK"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WU
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WU.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WU"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#WYNN
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/WYNN.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "WYNN"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#XEC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/XEC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "XEC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#XEL
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/XEL.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "XEL"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#XLNX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/XLNX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "XLNX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#XOM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/XOM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "XOM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#XRAY
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/XRAY.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "XRAY"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#XRX
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/XRX.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "XRX"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#YUM
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/YUM.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "YUM"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ZBH
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ZBH.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ZBH"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#ZION
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/ZION.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "ZION"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#^DJI
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/^DJI.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "DJI"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#^GSPC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/^GSPC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "GSPC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)


#^IXIC
stock <- read.csv(text = getURL("https://raw.githubusercontent.com/javierjr55/MSDS_6372_Project/master/Financial_Data/^IXIC.csv"), header = TRUE) [ ,1:2]
colnames(stock)[2] <- "IXIC"
SP500 <- merge(SP500, stock, by = "Date", all = TRUE)

```

Remove excess dates not necessary for for analysis
```{r}
#convert date to DATE object
SP500$Date = as.Date(SP500$Date)

#sort by ascending date
SP500 = arrange(SP500, Date)

#keep only data between 2002 and 2009
SP500 = filter(SP500, SP500$Date >= "2002-1-1" & SP500$Date < "2010-1-1")
```
Need stock companies with highest coefficients for the following indexes. 1 model per index.
^DJI (Dow Jones)
^GSPC (S&P 500)
^IXIC (Nasdaq)

```{r}
#Converting data frame with financial data to a time series
Index.ts<- ts(SP500)

#Plot Dow Jones
ggplot(data = SP500, aes(x = Date, y = DJI)) +
  geom_line(color = "#00AFBB", size = 1) +
  stat_smooth(
    color = "#FC4E07", fill = "#FC4E07",
    method = "loess"
  )

#Plot S&P 500
ggplot(data = SP500, aes(x = Date, y = GSPC)) +
  geom_line(color = "#00AFBB", size = 1) +
  stat_smooth(
    color = "#FC4E07", fill = "#FC4E07",
    method = "loess"
  )

#Plot NASDAQ
ggplot(data = SP500, aes(x = Date, y = IXIC)) +
  geom_line(color = "#00AFBB", size = 1) +
  stat_smooth(
    color = "#FC4E07", fill = "#FC4E07",
    method = "loess"
  )


# Separating indexes time serires data
#DJI  <- window(Index.ts[,445]) #Dow Jones
#GSPC <- window(Index.ts[,446]) #S&P 500
#IXIC <- window(Index.ts[,447]) #NASDAQ

decompose_DJI <-decompose(DJI)
plot(decompose_DJI)

decompose_GSPC <-decompose(GSPC)
plot(decompose_GSPC)

decompose_IXIC <-decompose(IXIC)
plot(decompose_IXIC)

fitholtdji <- holt(djits, alpha=.8, beta=.2, initial="simple", exponential=TRUE, h=5)
plot(fitholtdji, ylab="Daily Closing Price", xlab="Year",col="#377EB8", main="DJI Fit Holt Trend Method", fcol="red")
abline(v = 1997, untf = FALSE, col = "red")
accuracy(fitholtdji)
fitholtdji$model

fitholtGSPC <- holt(GSPCts, alpha=.8, beta=.2, initial="simple", exponential=TRUE, h=5)
plot(fitholtGSPC, ylab="Daily Closing Price", xlab="Year",col="#377EB8", main="GSPC Fit Holt Trend Method", fcol="red")
abline(v = 1997, untf = FALSE, col = "red")
accuracy(fitholtGSPC)
fitholtGSPC$model

fitholtIXIC <- holt(IXICts, alpha=.8, beta=.2, initial="simple", exponential=TRUE, h=5)
plot(fitholtIXIC, ylab="Daily Closing Price", xlab="Year",col="#377EB8", main="IXIC Fit Holt Trend Method", fcol="red")
abline(v = 1997, untf = FALSE, col = "red")
accuracy(fitholtIXIC)
fitholtIXIC$model

Index <- cbind(DJI, GSPC, IXIC)

```

```{r}
regfit.full = regsubsets(DJI~., SP500, nvmax = 30)
reg.summary <- summary(regfit.full)
plot(reg.summary$rsq, xlab = "Number of Companies", ylab = "RSquare", type = "1")
```